Periodic Traveling Waves in an Integro-Difference Equation With a Nonmonotone Growth Function and Strong Allee Effect

### 2021-07-13 Nestor_Li_manuscript_revision_7_13.tex
work

 Let $w_1$ and $w_2$ be two functions defined by
\begin{equation} \label{w1}
w_1(x) := \int_x^\infty \mtwo k(y) \, dy
\end{equation}
and
\begin{equation} \label{w2}
w_2(x) = \int_x^\infty \left( \mtwo k(y-x_\a) - (\mtwo-\m)k(y-x_\b)\right) \, dy 
\end{equation} 
where $x_\a$ and $x_\b$ constants constants given by
\begin{equation}
x_\a =\sup\left\{x\in\mathbb R\mid \int_{-\infty}^{x} k(y) \, dy \leq \frac{\a}{\mtwo} \right\}, \quad
x_\b =\sup\left\{x\in\mathbb R\mid \int_{-\infty}^{x} k(y) \, dy \leq \frac{\b}{\mtwo} \right\}
\end{equation}

\begin{lem} \label{lemmamain}
If $ || w_2 ||_\infty \leq \b $, then $w_1$ and $w_2$ satisfy
\begin{equation}
Q[w_1](x) = w_2(x)
\end{equation}
and
\begin{equation}
Q[w_2](x) = w_1(x-2c^*)
\end{equation}
for all $x\in\mathbb R$, where $c^*$ is a constant given by
\begin{equation}
c^* = \frac{1}{2} \sup\{x\in\mathbb R\mid w_2(x)\geq \a\}
\end{equation}
\end{lem}

%
%
%\begin{lem} \label{lemma0.5}
%$Q[w_1](x) = w_2(x)$ for all $x\in\mathbb R$.
%\end{lem}

\begin{proof}
$w_1$ is monotonically decreasing with $w_1(-\infty)=\mtwo$ and $w_1(\infty)=0$. It follows that $w_1(x)>\b$ for $x<x_\b$, $\a\leq w_1(x)\leq\b$ for $x_\b\leq x\leq x_\a$, and $w_1(x)<\a$ for $x>x_\a$. This yields
\begin{equation}
g(w_1(x)) = \begin{cases}
\m & x < x_\b \\
\mtwo & x_\b \leq x \leq x_\a \\
0 & x > x_\a
\end{cases}
\end{equation}
Applying the integro-difference operator yields
\begin{equation} \label{qw1calculation}
\begin{aligned}
Q[w_1](x) &= \int_{-\infty}^{\infty} k(x-y) g(w_1(y)) \, dy \\
&= \m \int_{-\infty}^{x_\b} k(x-y) \, dy + \mtwo \int_{x_\b}^{x_\a} k(x-y) \, dy \\
%&= \m \int_{x-x_\b}^{\infty} k(y) \, dy + \int_{x-x_\a}^{x-x_\b} k(y) \, dy \\
&= \mtwo \int_{x-x_\a}^{\infty} k(y) \, dy - (\mtwo-\m) \int_{x-x_\b}^{\infty} k(y) \, dy \\
&= \int_{x}^{\infty} \left( \mtwo k(y-x_\a)  - (\mtwo-\m)k(y-x_\b)\right) \, dy
\end{aligned} \end{equation}
%It can now be seen that replacing $x$ with $x-c^*$ in equation \eqref{w2} produces \eqref{qw1calculation}.
%\end{proof}

@@

%'\begin{proof}
By Hypothesis (H4), we have assumed that the integrand on the right hand side has at most one zero. We can now proceed in cases. $w_2(x)$ has either zero or one turning point(s). In the first case, $w_2(x)$ is monotonically decreasing and satisfies $w_2(x) \geq \a$ for $x \leq 2c^*$ and $w_2(x) < \a$ for $x > 2c^*$. In the second case, $w_2(x)$ has a unique turning point $x_0 \in \mathbb R$; it follows that $w_2(x)$ is monotonically increasing on $(-\infty,x_0)$ and monotonically decreasing on $(x_0,\infty)$, and $x_0$ is a global maximum. By the assumption $w_2(x)\leq\beta$ for all $x$, we have $w_2(x_0)\leq\beta$. It follows that $c^* \in (\frac{x_0}{2},\infty)$, and $w_2(x)$ satisfies $g(w_2(x))=1$ for $x<2c^*$ and $g(w_2(x)) = 0$ for $x>2c^*$. In both cases, we have

\begin{equation}
g(w_2(x)) = \begin{cases}
1 & x \leq 2c^* \\
0 & x > 2c^*
\end{cases}
\end{equation}

@@

\begin{thm} \label{theorem1}
If $\sup_{x\in\mathbb R}w_2(x)\leq \b$, then equation \eqref{q} has a periodic traveling wave solution given by %$(u_n)_{n=0}^{\infty}$ satisfying
%\begin{equation} \label{ptw}
%u_n(x) = \begin{cases}
%w_1(x-nc^*) & n \text{ even} \\
%w_2(x-nc^*) & n \text{ odd}
%\end{cases}
%\end{equation}

\begin{equation} \label{ptw}
u_n(x) = \begin{cases}
w_1(x-nc^*) & n \text{ even} \\
w_2(x-nc^*+c^*) & n \text{ odd}
\end{cases}
\end{equation}
for all $n \geq 0$.
\end{thm}

\begin{proof}
It suffices to show that equation \eqref{ptw} satisfies $u_{n+1}=Q[u_n]$ for all $n \geq 0$. If $n$ is even, then $n+1$ is odd, so $u_n(x)=w_1(x-nc^*)$ and $u_{n+1}(x)=w_2(x-nc^*)$. Applying the integro-difference operator, we obtain
\begin{equation} \begin{aligned}
Q[u_n](x) &= Q[w_1](x-nc^*) \\
&= w_2(x-nc^*) \\
&= u_{n+1}(x)
\end{aligned} \end{equation}
by \eqref{w2}. On the other hand, if $n$ is odd, then $n+1$ is even, so $u_n(x)=w_2(x-nc^*+c^*)$ and $u_{n+1}(x)=w_1(x-nc^*-c^*)$. Applying the operator, we get
\begin{equation} \begin{aligned}
Q[u_n](x) &= Q[w_2](x-nc^*+c^*) \\
&= w_1(x-nc^*-c^*) \\
&= u_{n+1}(x)
\end{aligned} \end{equation}
by Lemma \ref{lemmamain}.
\end{proof}

%For convenience, we will switch the index and consider the cases $u_{2n}$ and $u_{2n+1}$ separately. The basic case, $u_1 = Q[u_0]$, follows immediately from definition \ref{w2}. This proves the first half. Next, we have $u_2(x)=w_1(x-2c^*)$, which follows by Lemma \ref{lemma1}.
%
%For the inductive step, suppose $u_{2n+1}=Q[u_{2n}]$ and $u_{2n+2}=Q[u_{2n+1}]$ for some $n\geq 0$. We only need to show $u_{2n+3}=Q[u_{2n+2}]$. We have
%\begin{equation} \begin{aligned}
%u_{2n+3}(x) &= w_2(x-2nc^*-2c^*) \\
%&= Q^2[w_2](x-2nc^*) \\
%&= Q^2[u_{2n+1}](x) \\ 
%&= Q[u_{2n+2}](x)
%\end{aligned} \end{equation}
% \end{proof}

@@

For every $n\geq 1$, let $c_n = \xi_n - \xi_{n-1}$.

@@

\begin{thm}  \label{theorem2}
If $\sup_{x\in\mathbb R}w_2(x)\leq \b$, then for all $\epsilon>0$, the sequence \ref{ptw} satisfies
\begin{equation}
\lim_{n\to\infty}\inf_{x<2n(c^*-\epsilon)}u_{2n}(x)=1
\end{equation}
and
\begin{equation}
\lim_{n\to\infty}\inf_{x<2n(c^*-\epsilon)}u_{2n+1}(x)=\m
\end{equation}
and 
\begin{equation}
\lim_{n\to\infty}\sup_{x>n(c^*+\epsilon)}u_n(x)=0.
\end{equation}
\end{thm}

@@

@@

Let $\mathbf 1_{[-r,r]}$ denote the indicator function on $[-r,r]$. Suppose $u_0$ is a continuous function with compact support, and suppose $u_0$ satisfies $\a \leq u_0(x) \leq \b$ for $|x| \leq r$ and $u_0(x) < \a$ otherwise. It follows that
$$ g(u_0(x)) = \mathbf 1_{[-r_0,r_0]}(x) $$
We have
$$ Q[u_0](x) = (k*(g \circ u_0))(x) = K(x+r_0) - K(x-r_0) $$
Assuming $r_0$ is large enough so that $ Q[u_0](x) = 2K(r_0)-1 \geq \b$, it follows that
$$ g(Q[u_0](x)) = \begin{cases}
n_1 & |x| < r_1 \\
n_2 & r_1 \leq |x| \leq r_2 \\
0 & |x| > r_2
\end{cases} $$
It follows that
$$ Q^2 [u_0] (x) = n_2 \int_{-r_2}^{r_2} k(x-y)\,dy - (n_2-n_1) \int_{-r_1}^{r_1} k(x-y) \, dy $$
$$ = n_2 K(x+r_2) - n_2K(x-r_2) - (n_2-n_1) K(x+r_1) + (n_2-n_1) K(x-r_1) $$
Taking the derivative, we find
$$ \frac{d}{dx} Q^2 [u_0](x) = n_2 k(x+r_2) - n_2k(x-r_2) - (n_2-n_1) k(x+r_1) + (n_2-n_1) k(x-r_1) $$

We now require the following hypothesis on the disperal kernel:

@@

If hypothesis (H5) holds, we can then deduce that $\frac{d}{dx}Q^2[u_0]$ has at most 3 zero-crossings, hence, $Q^2[u_0]$ has at most 3 turning points. This leaves only two cases: either $Q^2[u_0]$ has a single turning point at $x=0$, or $Q^2[u_0]$ has 3 turning points, one at $x=0$, and two diametrically opposed turning points $+t$ and $-t$. In both cases, there is a unique $r_2>0$ satisfying $Q^2[u_0](x) \geq \a$ for $|x| \leq r_2$ and $Q^2[u_0](x) < \a$ otherwise. If $r_2 < r$, then the conclusion does not follow. But if $r_2 \geq r$, then the

The next theorem concerns the spreading behavior of solutions to the IDE \eqref{q} with compactly supported initial data.

@@

\subsection{Blossoming solution}

In addition to the behavior mentioned earlier, we noticed the phenomena of blossoming solution. Whenever

@@

with $x_a = F(a)$, $x_b=F(b)$, and
F(p) = \begin{cases} -\ln(2p) &p \leq \frac{1}{2} \\ \ln(2-2p) & p > \frac{1}{2} \end{cases}

@@

We can also explicitly calculate the speed of the wave given by
\begin{equation} \label{c}
c^* = \begin{cases}
1 - 2a & \text{if } a \leq b/2, \\
1 -b + \frac{b - 2a}{m} & \text{if }a > b/2.
\end{cases}
\end{equation}
\end{ex}
\begin{rem}
$w_1(x)$ is positive for $x<1$ and zero for $x\geq1$, and $w_2(x)$ is positive for $x<2-2a$ and zero for $x\geq 2-2a$. Thus, $\eqref{q}$ has a traveling wave with wave profiles $w_1(x)$ and $w_2(x)$, intermediate wave speeds $c_1=1-2a$ and $c_2=2c^*-c_1$,  and average wave speed  $c^*$.  It is easily seen that $c_1=c_2$ if $a \leq b/2$, and $|c_1-c_2|=(2\alpha-\beta)(1-\frac{1}{m})>0$ if $a>b/2$. So for $a>b/2$, the traveling wave is periodic with two different intermediate wave speeds. Furthermore, the difference between these two intermediate speeds is increasing in $a$, decreasing in $b$, and increasing in $m$. This behavior is illustrated with two difference choices of parameters in Figure \ref{fig:wavespeed}.
\end{rem}

>>>>

\begin{lem} \label{lemmamain}
Let $w(x) = \int_x^\infty k(y) \, dy$. Define
\begin{equation}
c^* = \frac{1}{2} \sup \{ x\in\mathbb R | Q[\mtwo w](x) \geq \a \}
\end{equation}
Let $w_1(x) = w(x)$ and $w_2(x) = Q[w](x+c^*)$. If $|| w_2 ||_\infty \leq \b $, then $w_1$ and $w_2$ satisfy
\begin{equation} \label{lemma1claim1}
Q[w_1](x) = w_2(x-c^*)
\end{equation}
and
\begin{equation}\label{lemma1claim2}
Q[w_2](x) = w_1(x-c^*)
\end{equation}
for all $x \in \mathbb R$.
\end{lem}

%
%\begin{lem} \label{lemma0.5}
%$Q[w_1](x) = w_2(x)$ for all $x\in\mathbb R$.
%\end{lem}

\begin{proof}
Equation \ref{lemma1claim1} follows directly from the definition of $w_2(x)$.

To prove \ref{lemma1claim2}, observer that $w_1$ is monotonically decreasing with $w_1(-\infty)=\mtwo$ and $w_1(\infty)=0$. It follows that $w_1(x)>\b$ for $x<x_\b$, $\a\leq w_1(x)\leq\b$ for $x_\b\leq x\leq x_\a$, and $w_1(x)<\a$ for $x>x_\a$, where $x_a$ and $x_b$ are the solutions of
\begin{equation}
w_1(x_\a) = \a, \quad w_1(x_\b) = \b
\end{equation}
This yields
\begin{equation}
g(w_1(x)) = \begin{cases}
\m & x < x_\b \\
\mtwo & x_\b \leq x \leq x_\a \\
0 & x > x_\a
\end{cases}
\end{equation}
Applying the integro-difference operator yields
\begin{equation} \label{qw1calculation}
\begin{aligned}
Q[w_1](x) %&= \int_{-\infty}^{\infty} k(x-y) g(w_1(y)) \, dy \\
&= \m \int_{-\infty}^{x_\b} k(x-y) \, dy + \mtwo \int_{x_\b}^{x_\a} k(x-y) \, dy %\\
\end{aligned} \end{equation}
%&= \m \int_{x-x_\b}^{\infty} k(y) \, dy + \int_{x-x_\a}^{x-x_\b} k(y) \, dy \\
%&= \mtwo \int_{x-x_\a}^{\infty} k(y) \, dy - (\mtwo-\m) \int_{x-x_\b}^{\infty} k(y) \, dy \\
Using a substitution on both integrals yields equation \eqref{w2}, proving the first part of the lemma.
%It can now be seen that replacing $x$ with $x-c^*$ in equation \eqref{w2} produces \eqref{qw1calculation}.
%\end{proof}

@@

%'\begin{proof}
To prove the second half, we differentiate $w_2$ with respect to $x$:
\begin{equation} \label{dqw1}
\frac{dw_2}{dx} = \mtwo k(x-x_\a) - (\mtwo-\m) k(x-x_\b)
\end{equation}
A transformation of coordinates shows that equation \eqref{dqw1} is proportional to $k(x) - \frac{\mtwo-\m}{\mtwo} k(x+x_\a-x_\b)$; by hypothesis (H4), $\frac{dw_2}{dx}$ has at most one real zero.

It can be shown by cases that $w_2$ is either monotonically decreasing or has a unique turning point $x_0 \in \mathbb R$. In both cases, the curve $u=w_2(x)$ crosses the horizontal line $u=\a$ exactly once at the point $x=2c^*$. In the latter case, we utilize the assumption that $|| w_2 ||_\infty \leq \b$ . In all cases,

%By Hypothesis (H4), we have assumed that the integrand on the right hand side has at most one zero. We can now proceed in cases. $w_2(x)$ has either zero or one turning point(s). In the first case, $w_2(x)$ is monotonically decreasing and satisfies $w_2(x) \geq \a$ for $x \leq 2c^*$ and $w_2(x) < \a$ for $x > 2c^*$. In the second case, $w_2(x)$ has a unique turning point $x_0 \in \mathbb R$; it follows that $w_2(x)$ is monotonically increasing on $(-\infty,x_0)$ and monotonically decreasing on $(x_0,\infty)$, and $x_0$ is a global maximum. By the assumption $w_2(x)\leq\beta$ for all $x$, we have $w_2(x_0)\leq\beta$. It follows that $c^* \in (\frac{x_0}{2},\infty)$, and $w_2(x)$ satisfies $g(w_2(x))=1$ for $x<2c^*$ and $g(w_2(x)) = 0$ for $x>2c^*$. In each case, we have
%%
\begin{equation}
g(w_2(x)) = \begin{cases}
1 & x \leq 2c^* \\
0 & x > 2c^*
\end{cases}
\end{equation}

@@

\begin{thm} \label{theorem1}
Let $u_n(x)$ be a sequence of functions defined by
\begin{equation}
u_n(x) = \begin{cases} \label{ptw}
w_1(x-nc^*) & n \text{ even} \\
w_2(x-nc^*) & n \text{ odd}
\end{cases} \end{equation}
If $|| w_2 ||_\infty \leq \b $, then $u_n(x)$ satisfies $u_{n+1}(x) = Q[u_n](x)$ for all $n\geq 0$.
\end{thm}

\begin{proof}
Let $n \geq 0$. If $n$ is even, then $n+1$ is odd, so $u_n(x)=w_1(x-nc^*)$ and $u_{n+1}(x)=w_2(x-nc^*)$. Applying the integro-difference operator, we obtain
\begin{equation} \begin{aligned}
Q[u_n](x) &= Q[w_1](x-nc^*) \\
&= w_2(x-nc^*) \\
&= u_{n+1}(x)
\end{aligned} \end{equation}
by \eqref{w2}. On the other hand, if $n$ is odd, then $n+1$ is even, so $u_n(x)=w_2(x-nc^*+c^*)$ and $u_{n+1}(x)=w_1(x-nc^*-c^*)$. Applying the operator, we get
\begin{equation} \begin{aligned}
Q[u_n](x) &= Q[w_2](x-nc^*+c^*) \\
&= w_1(x-nc^*-c^*) \\
&= u_{n+1}(x)
\end{aligned} \end{equation}
by Lemma \ref{lemmamain}.
\end{proof}

@@

$$
w_i(x) = \int_\Omega k(x-y+2c^*) g\left( \int_\Omega k(y-y') g(w_i(y')) \, dy' \right) \, dy
$$
For every $n\geq 1$, let $c_n = \xi_n - \xi_{n-1}$.

@@

\begin{thm}  \label{theorem2}
If $||w_2|| \b$, then for all $\epsilon>0$, the sequence \ref{ptw} satisfies
\begin{equation}
\lim_{n\to\infty}\inf_{x<2n(c^*-\epsilon)}u_{2n}(x)=\mtwo
\end{equation}
and
\begin{equation}
\lim_{n\to\infty}\inf_{x<2n(c^*-\epsilon)}u_{2n+1}(x)=\m
\end{equation}
and 
\begin{equation}
\lim_{n\to\infty}\sup_{x>n(c^*+\epsilon)}u_n(x)=0.
\end{equation}
\end{thm}

@@

\textbf{Note: this section contains incomplete results.}

@@

Let $\chi_{[-r,r]}$ denote the indicator function on $[-r,r]$. Suppose $u_0$ is a continuous function with compact support, and suppose $u_0$ satisfies $\a \leq u_0(x) \leq \b$ for $|x| \leq r$ and $u_0(x) < \a$ otherwise. It follows that
$$ g(u_0(x)) = \chi_{[-r,r]}(x) $$

%
%Let $u_n(x)$ be a sequence of continuous functions. For every $c \in \mathbb R$, define the sequence $a_n(x,c)$ by
%$$ a_n(x,c) = u_n(x+nc) $$
%Now, define
%$$ a(x,c) = \limsup_{n\to\infty} a_n(x,c). $$
%Note that since $a_n$ is bounded, this quantity must be finite. We say the rightware spreading speed of $u_0$ is defined by
%$$ c^*_+ = \inf \{ c \in \mathbb R \mid \lim_{x\to\infty} a(x,c) = 0 \} $$
%
%\begin{lem}
%If $||w_2||_\infty\leq\b$, the sequence \eqref{ptw} has a rightward spreading speed of $c^*$.
%\end{lem}
%
%\begin{proof}
%We have
%$$ a_n(x,c) = \begin{cases}
%w_1(x + n(c-c^*))  & n \text{ even} \\
%w_2(x + n(c-c^*)) & n \text{ odd}
%\end{cases} $$
%Thus,
%$$ \begin{aligned}
%a(x,c) &= \limsup_{n\to\infty} a_n(x,c) \\
%&= \limsup_{n\to\infty} \max \{ w_1(x + n(c-c^*)), w_2(x + n(c-c^*)) \} \\
%&= \begin{cases}
%1 & c < c^* \\
%\max\{w_1(x),w_2(x)\} & c=c^* \\
%0 & c>c^*
%\end{cases} \end{aligned} $$
%Taking the limit as $x\to\infty$,
%$$ a(\infty,c) = \begin{cases}
%1 & c < c^* \\
%0 & c \geq c^*
%\end{cases} $$
%\end{proof}

For a given $r \geq 0$, let $\phi(x,r) = \chi_{[-r,r]}(x)$, or simply $\phi_r$ for brevity. Define the operator $R[u] = g\left( Q[k*u](x) \right)$.

\begin{equation}
R[u](x) = g\left( \int k(x-y) g\left( \int k(y-z) u(z) \, dz \right) \, dy \right)
\end{equation}

\begin{lem}
Let $u_n(x)$ be a sequence of functions satisfying $u_{n+1}(x)=Q[u_n](x)$ for all $n \geq 0$ with initial condition $u_0 \in C(\mathbb R; [0,1])$. Then $u_{2n}(x) = (k*R^{n-1}[g\circ u])(x)$ for all $n\geq1 $.
\end{lem}

\begin{lem}
For sufficiently large $r \geq 0$, we have $R[\phi_r] = \phi_{r+\delta(r)}$, where $\delta(r)$ is a scalar function of $r$. It can be expressed as
$$ \delta(r) = \int R[\phi_r](x)  \, dx $$
\end{lem}

\begin{proof}
We have
$$ (k*\phi_r)(x) = K(x+r) - K(x-r) $$
Note that $(k*\phi_r)(0) = 2K(r)-1$, assuming a symmetryic dispersal kernel. Thus, assuming $\frac{d}{dx}(k*\phi_r)$ has at most one zero, a lower bound of $r \geq K^{-1}\left(\frac{\b+1}{2}\right)$ guarantees 
$$ R[\phi_r] = \begin{cases}
n_1 & |x| < r_1 \\
n_2 & r_1 \leq |x| \leq r_2 \\
0 & |x| > r_2
\end{cases} $$
\end{proof}
for some $r_2 > r_1 \geq 0$.

Applying the convolution operator to this expression yields
$$ k*R[\phi_r] (x) = n_2 \int_{-r_2}^{r_2} k(x-y)\,dy - (n_2-n_1) \int_{-r_1}^{r_1} k(x-y) \, dy $$
$$ = n_2 \left[ K(x+r_2) - K(x-r_2)  \right] - (n_2-n_1) \left[ K(x+r_1) - K(x-r_1) \right] $$
Taking the derivative, we find
$$ \frac{d}{dx} \left[ k*R[\phi_r] \right] = n_2 \left[ k(x+r_2) - k(x-r_2)  \right] - (n_2-n_1) \left[ k(x+r_1) - k(x-r_1)\right] $$
We now require the following hypothesis on the disperal kernel:

@@

If hypothesis (H5) holds, we can then deduce that $k*R[\phi_r]$ has at most 3 turning points. This leaves only two cases: either $k*R[\phi_r]$ has a single turning point at $x=0$, or has 3 turning points, one at $x=0$, and two diametrically opposed turning points $+t$ and $-t$. In both cases, there is a unique $r_3>0$ satisfying $(k*R[\phi_r])(x) \geq \a$ for $|x| \leq r_3$ and $(k*R[\phi_r])(x) < \a$ otherwise.

\textbf{Note: the above section contains unfinished proofs.}

@@

@@

with $x_a = F(a)$, $x_b=F(b)$, and
\begin{equation}
F(p) = \begin{cases} -\ln(2p) &p \leq \frac{1}{2} \\ \ln(2-2p) & p > \frac{1}{2} \end{cases}
\end{equation}

@@

We can also explicitly calculate the speed of the wave given by
\begin{equation} \label{clinear}
c^* = \begin{cases}
1 - 2a & \text{if } a \leq b/2, \\
1 -b + \frac{b - 2a}{m} & \text{if }a > b/2.
\end{cases}
\end{equation}
\end{ex}
\begin{rem}
$w_1(x)$ is positive for $x<1$ and zero for $x\geq1$, and $w_2(x)$ is positive for $x<2-2a$ and zero for $x\geq 2-2a$. Thus, $\eqref{q}$ has a traveling wave with wave profiles $w_1(x)$ and $w_2(x)$, intermediate wave speeds $c_1=1-2a$ and $c_2=2c^*-c_1$,  and average wave speed  $c^*$.  It is easily seen that $c_1=c_2$ if $a \leq b/2$, and $|c_1-c_2|=(2\alpha-\beta)(1-\frac{1}{m})>0$ if $a>b/2$. So for $a>b/2$, the traveling wave is periodic with two different intermediate wave speeds. Furthermore, the difference between these two intermediate speeds is increasing in $a$, decreasing in $b$, and increasing in $m$. This behavior is illustrated with two difference choices of parameters in Figure \ref{fig:wavespeed}.
\end{rem}
